---
title: "scCODE-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{scCODE-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(scCODE)
```
#load data

### This should be a matrix n genes by N cells, rowname should be gene names, colnames shall be cell names
datarow<-data_sample 
### The group information of cells, a factor. 1 for celltype 1, 2 for cell type 2
group<-group_sample 

#run CODE

##light = True, runing CODE in a light version, saves time.

results<-run_CODE(data_sample,group_sample,light = TRUE) 


## The results is a list, which contains the AUCC and CDO matrix of methods, a conclusion of the optimal filtering method and DE method, and the DE results(DE gene name, p-adjust,fc) of the optimal method.

### ?run_CODE for help

### ?CODE.BPSC (t_test,MAST...) for help of DE methods. ?CODE.filter_OGFSC for help of filtering methods.
